---
title: "Homework 5"
output: github_document
---

```{r}
library(tidyverse)
library(patchwork)
library(readxl)
library(broom)
```

```{r setup}

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1 

Read data
```{r} 
homicide_df = 
  read_csv("./data/homicide_data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit
```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

```

Prop test for a single city
```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate
```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r, error = TRUE}
city_prop_test = function(df) 
homicide_df = 
  read_csv("./data/homicide_data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```

## Problem 2

import one dataset 

```{r}
data_1 = read_csv("./longitudinal_data/con_01.csv")
```


```{r}

path_df = 
  tibble(
    path = list.files("longitudinal_data")
  ) %>% 
  mutate(
    path = str_c("longitudinal_data/", path),
data = map(path, read_csv)) 


```

```{r}
path_df_unested= 
path_df %>% 
  mutate(
   path =  str_remove_all(path, "longitudinal_data/"),
path =  str_remove_all(path, ".csv"),
    path = str_replace(path, "con", "control"), 
     path = str_replace(path, "exp", "experiment"))%>%
   separate(path, into = c("control_arm", "subject_id"))%>% 
  unnest (data) %>% 
  
  pivot_longer(week_1: week_8, 
               names_to="week", 
               values_to = "value") 


```
Spaghetti plot
```{r}


ggplot(path_df_unested, aes(x=week, y=value, group = subject_id,color= subject_id)) +
  geom_line() +
  theme_bw() + facet_grid(.~control_arm) +
  labs(title = "Observations on each subject over time")
```

### Comment on differences between groups. 

Overall the experiment arm seems to have increasing positive values, on average, as the weeks progress. The Control arm on the other hand seems to have decreasing or stable values as the weeks progress, half of the observations seem to have negative values at some points. 


## Problem 3


```{r}
ttest = function(n=30, mu = 0, sd = 5) {
sample_data = tibble(
x = rnorm(n=30, mean = mu, sd = 5),
)
sample_data %>%
t.test() %>%
  broom::tidy()
}
```

Test ttest function 
```{r}
ttest_results = 
  rerun(5000, ttest(30, 0, 5))%>%
  bind_rows()
```


```{r}
  mu = 
  list ( 
    "mu_0" = 0, 
    "mu_1" = 1, 
    "mu_2" = 2, 
    "mu_3" = 3, 
    "mu_4" = 4, 
    "mu_5" = 5,
    "mu_6" = 6 
    )

output_ttest = vector("list", length = 7)
for (i in 1:7) {
output_ttest[[i]] = rerun(5000, ttest(mu = mu[[i]])) %>%
bind_rows() 
}

```


```{r}
data_plot1 = 
  bind_rows (output_ttest, .id = "mu")%>%
  select(mu, estimate, p.value) %>%
mutate (cutoff = case_when(p.value < 0.05 ~ "Reject", p.value >=0.05 ~ "Fail to Reject")) %>%
mutate(
mu = recode (mu, "1" = "0", "2" = "1", "3" = "2", "4" = "3","5" = "4","6" = "5",
"7" = "6")) 

```

```{r}
data_plot1 %>%
  group_by(mu) %>%
  summarize(
n = n(),
power = sum(p.value < 0.05)/n) %>%
  ggplot(aes(x = mu, y = power)) + geom_line() +geom_point() + labs(title = "Proportion of Times the Null was Rejected") 
```

Shown above in the figure we see that as mu increases so does the power. This means that the probability of rejecting the null increases as the effect size increases. 


```{r}
plot_estimate = 
data_plot1 %>%
  group_by(mu) %>%
  summarize(
    mu_hat = mean(estimate))%>%
  ggplot(aes(x = mu, y = mu_hat)) + geom_line() + geom_point() + labs(
    title =  "Plot 1: True Mu by Average Est Mu",
    x= "true value of μ",
    y = "average estimate of μ̂"  )
```

```{r}
plot_avg_estimate = 
data_plot1 %>%
  group_by(mu) %>%
  filter(cutoff=="Reject") %>%
  summarize(
    mu_hat = mean(estimate))%>%
  ggplot(aes(x = mu, y = mu_hat)) + geom_line() +geom_point() + labs(
    title =  "Plot 2:Null Rejected, True Mu by Average Est Mu,",
    x= "true value of μ",
    y = "average estimate of μ̂"  )
```

Combine plots 
```{r}
plot_estimate + plot_avg_estimate 
```

Plot 1 shows the average estimated mu and true value of mu. 

Plot 2 shows the average estimated mu and true value of mu for observations in which the null was rejected. The sample average of μ̂ across the tests for which the null is rejected is not approximately equal to the true value of μ. This is because as the power decreases the average estimates get further away from the true mean and vice versa when the power increase.  


